\textbf{{\Large {Recursive algorithms, branching coefficients affine algebras and applications}}}

### 2010-05-12 AffineLieAlgebras/InformalNotes/article.tex
Illustrations regenerated

Using the recurrent relation for the anomalous branching coefficients we get the following result
\begin{figure}[ph]
  \centering
  \includegraphics[width=130mm]{AffineB2_A1_branching.pdf}
  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{B_2}$}
  \label{fig:AffineB2_A1_branching}
\end{figure}

Selecting the elements inside the main Weyl chamber of the subalgebra $\hat{A_1}$ we get the following results for the branching coefficients up to twelfth grade
\begin{multline}
  \label{eq:28}
  L^{w_1}_{\hat{B_2}\downarrow \hat{A_1}}=2 L_{\hat{A_1}}^{w_1}(0)\oplus 1 L_{\hat{A_1}}^{w_0}(0)\oplus 4 L_{\hat{A_1}}^{w_0}(-1)\oplus\\
    2 L_{\hat{A_1}}^{w_1}(-1)\oplus 8 L_{\hat{A_1}}^{w_0}(-2)\oplus
    8 L_{\hat{A_1}}^{w_1}(-2)\oplus 15 L_{\hat{A_1}}^{w_0}(-3)\oplus\\
    12 L_{\hat{A_1}}^{w_1}(-3)\oplus 26 L_{\hat{A_1}}^{w_1}(-4)\oplus
    29 L_{\hat{A_1}}^{w_0}(-4)\oplus 51 L_{\hat{A_1}}^{w_0}(-5)\oplus\\
    42 L_{\hat{A_1}}^{w_1}(-5)\oplus 78 L_{\hat{A_1}}^{w_1}(-6)\oplus
    85 L_{\hat{A_1}}^{w_0}(-6)\oplus 120 L_{\hat{A_1}}^{w_1}(-7)\oplus\\
    139 L_{\hat{A_1}}^{w_0}(-7)\oplus 202 L_{\hat{A_1}}^{w_1}(-8)\oplus
    222 L_{\hat{A_1}}^{w_0}(-8)\oplus 306 L_{\hat{A_1}}^{w_1}(-9)\oplus\\
    346 L_{\hat{A_1}}^{w_0}(-9)\oplus 530 L_{\hat{A_1}}^{w_0}(-10)\oplus
    482 L_{\hat{A_1}}^{w_1}(-10)\oplus 714 L_{\hat{A_1}}^{w_1}(-11)\oplus\\
    797 L_{\hat{A_1}}^{w_0}(-11)\oplus 1080 L_{\hat{A_1}}^{w_1}(-12)\oplus
    1180 L_{\hat{A_1}}^{w_0}(-12)
\end{multline}
This result can be expressed using the power series expansion of the branching functions \cite{kac1990idl}.
\begin{eqnarray}
  \label{eq:29}
  \begin{array}{cc}
    b^{(w_1)}_{0}= & 1 + 4\,q^{1}+ 8\,q^{2}+ 15\,q^{3}+ 29\,q^{4}+ 51\,q^{5}+ 85\,q^{6}+ 139\,q^{7}+\\
     &222\,q^{8}+ 346\,q^{9}+ 530\,q^{10}+ 797\,q^{11}+ 1180\,q^{12}+\dots\\
  \end{array}\\
  \begin{array}{cc}
    b^{(w_1)}_{1}= &2+2\,q^{1}+8\,q^{2}+12\,q^{3}+26\,q^{4}+42\,q^{5}+78\,q^{6}+120\,q^{7}+\\
    & 202\,q^{8}+306\,q^{9}+482\,q^{10}+714\,q^{11}+1080\,q^{12}+\dots
  \end{array}
\end{eqnarray}
Here the lower index of the branching function denotes the number of the corresponding $\hat{A_1}$ fundamental weight $w_0=\lambda_0=(0,1,0),\; w_1=\alpha/2=(1,1,0)$.

@@

Let us consider the representation with the highest weight $w_0=(0,0;1;0)$ in details. Here the first two components are the Dynkin indices (coordinates in the fundamental weights basis) of the finite part of the weight.

@@

Using the recurrent relation for the anomalous branching coefficients we get the result presented in Figure \ref{fig:AffineA2_A1_branching}. 
\begin{figure}[p]
  \centering
  \includegraphics[width=130mm]{AffineA2_A1_branching.pdf}
  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{A_2}$}
  \label{fig:AffineA2_A1_branching}
\end{figure}

We see that inside the main Weyl chamber of $\hat{A}_1$ there are only two non-zero anomalous weights. (Show the Weyl chambers on the Figure.) These are the branching coefficients. So the finite reducibility theorem holds and we get the decomposition
\begin{equation}
  \label{eq:43}
  L^{(0,0;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(0;4;0)}\oplus L_{\hat{A_1}}^{(4;4;0)]}.
\end{equation}

@@

We limit our computation by the fifth grade.

\begin{figure}[h!tb]
  \includegraphics[width=150mm]{A1+A1-A3_anom.pdf}
  \caption{Projected anomalous weights for $L^{\omega_1}_{A_3}$}
  \label{fig:A1+A1-A3_anom}
\end{figure}

>>>>

Using the recurrent relation for the anomalous branching coefficients we get the following result, presented at the Figure \ref{fig:AffineB2_A1_branching}. Dotted area represents the main Weyl chamber of the algebra $\hat{A}_1$.
\begin{figure}[ph]
  \centering
  \includegraphics[width=110mm]{AffineB2_A1_branching.pdf}
  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{B_2}$}
  \label{fig:AffineB2_A1_branching}
\end{figure}

Selecting the elements inside the main Weyl chamber of the subalgebra $\hat{A_1}$ we get for the branching coefficients up to twelfth grade
\begin{multline}
  \label{eq:28}
  L^{w_1}_{\hat{B_2}\downarrow \hat{A_1}}=2 L_{\hat{A_1}}^{w_1}(0)\oplus 1 L_{\hat{A_1}}^{w_0}(0)\oplus 4 L_{\hat{A_1}}^{w_0}(-1)\oplus\\
    2 L_{\hat{A_1}}^{w_1}(-1)\oplus 8 L_{\hat{A_1}}^{w_0}(-2)\oplus
    8 L_{\hat{A_1}}^{w_1}(-2)\oplus 15 L_{\hat{A_1}}^{w_0}(-3)\oplus\\
    12 L_{\hat{A_1}}^{w_1}(-3)\oplus 26 L_{\hat{A_1}}^{w_1}(-4)\oplus
    29 L_{\hat{A_1}}^{w_0}(-4)\oplus 51 L_{\hat{A_1}}^{w_0}(-5)\oplus\\
    42 L_{\hat{A_1}}^{w_1}(-5)\oplus 78 L_{\hat{A_1}}^{w_1}(-6)\oplus
    85 L_{\hat{A_1}}^{w_0}(-6)\oplus 120 L_{\hat{A_1}}^{w_1}(-7)\oplus\\
    139 L_{\hat{A_1}}^{w_0}(-7)\oplus 202 L_{\hat{A_1}}^{w_1}(-8)\oplus
    222 L_{\hat{A_1}}^{w_0}(-8)\oplus 306 L_{\hat{A_1}}^{w_1}(-9)\oplus\\
    346 L_{\hat{A_1}}^{w_0}(-9)\oplus 530 L_{\hat{A_1}}^{w_0}(-10)\oplus
    482 L_{\hat{A_1}}^{w_1}(-10)\oplus 714 L_{\hat{A_1}}^{w_1}(-11)\oplus\\
    797 L_{\hat{A_1}}^{w_0}(-11)\oplus 1080 L_{\hat{A_1}}^{w_1}(-12)\oplus
    1180 L_{\hat{A_1}}^{w_0}(-12)
\end{multline}
This result can be expressed using the power series expansion of the branching functions \cite{kac1990idl}.
\begin{eqnarray}
  \label{eq:29}
  \begin{array}{cc}
    b^{(w_1)}_{0}= & 1 + 4\,q^{1}+ 8\,q^{2}+ 15\,q^{3}+ 29\,q^{4}+ 51\,q^{5}+ 85\,q^{6}+ 139\,q^{7}+\\
     &222\,q^{8}+ 346\,q^{9}+ 530\,q^{10}+ 797\,q^{11}+ 1180\,q^{12}+\dots\\
  \end{array}\\
  \begin{array}{cc}
    b^{(w_1)}_{1}= &2+2\,q^{1}+8\,q^{2}+12\,q^{3}+26\,q^{4}+42\,q^{5}+78\,q^{6}+120\,q^{7}+\\
    & 202\,q^{8}+306\,q^{9}+482\,q^{10}+714\,q^{11}+1080\,q^{12}+\dots
  \end{array}
\end{eqnarray}
Here the lower index of the branching function denotes the number of the corresponding $\hat{A_1}$ fundamental weight $w_0=\lambda_0=(0,1,0),\; w_1=\alpha/2=(1,1,0)$.

@@

Let us consider the representation with the highest weight $w_0=(0,0;1;0)$ in details. Here the first two components are the Dynkin indexes (coordinates in the fundamental weights basis) of the finite part of the weight.

@@

Using the recurrent relation for the anomalous branching coefficients we get the result presented in Figure \ref{fig:AffineA2_A1_branching}. 
\begin{figure}[ph]
  \centering
  \includegraphics[width=110mm]{AffineA2_A1_branching.pdf}
  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{A_2}$}
  \label{fig:AffineA2_A1_branching}
\end{figure}

We see that inside the main Weyl chamber of $\hat{A}_1$, which is dotted at the Figure \ref{fig:AffineA2_A1_branching}, there are only two non-zero anomalous weights. These are the branching coefficients. So the finite reducibility theorem holds and we get the decomposition
\begin{equation}
  \label{eq:43}
  L^{(0,0;1;0)}_{\hat{A_2}\downarrow \hat{A_1}}= L_{\hat{A_1}}^{(0;4;0)}\oplus L_{\hat{A_1}}^{(4;4;0)]}.
\end{equation}

@@

We limit our computation by the fifth grade.
\begin{figure}[h!tb]
  \includegraphics[width=170mm]{A1+A1-A3_anom.pdf}
  \caption{Projected anomalous weights for $L^{\omega_1}_{A_3}$}
  \label{fig:A1+A1-A3_anom}
\end{figure}
